On the combination of Set Functions and Failures

### 2012-04-03 docs/Set_Functions_and_Failures.tex
Minor corrections to the Set Functions semantics paper

\usepackage{listings}

\title{On the combination of Set Functions and Failures}

@@

sizes :: Size
sizes = Small ? Big

getSmallest | isEmpty (set1 isSmallest aSize) = aSize
  where aSize = sizes

isSmallest size | size < sizes = size
\end{lstlisting}

This program is a straightforward implementation of the intuitive definition
that a value from a non-deterministic expression is the smallest if there
is no smaller one. And with our implementation of Set Function it works
just fine, there is only the one result \lstinline{Small}.

No let's change the definition of \lstinline{getSmallest}:

\begin{lstlisting}
getSmallest 
 | isEmpty (set1 isSmallest (aSize =:= sizes &> aSize))
 = aSize
 where aSize = size
\end{lstlisting}

@@

\textit{A set that contains only failing computations that stem from an argument
        is a failing computation it is the set without any failing computations
        otherwise}

>>>>

\usepackage{listings}
\lstset{basicstyle=\small\ttfamily}

\title{On the combination of Set Functions and Failures}
\author{Fabian Reck}

@@

aSize :: Size
aSize = Small ? Big

getSmallest | isEmpty (set1 smallerThan size) = size
  where size = aSize

smallerThan size | anotherSize < size = anotherSize
  where anotherSize = aSize
\end{lstlisting}

This program is a straightforward implementation of the intuitive definition
that a value from a non-deterministic expression is the smallest if there
is no smaller one. And with our implementation of Set Functions it works
just fine, there is only the one result \lstinline{Small}.

Now let's change the definition of \lstinline{getSmallest}:

\begin{lstlisting}
getSmallest 
 | isEmpty (set1 smallerThan (size =:= aSize &> size))
 = size
 where size = aSize
\end{lstlisting}

@@

% TODO: Definition?
\begin{quote}
A set that contains only failing computations that stem from an argument
is a failing computation.
Otherwise, it is the set without any failing computations.
\end{quote}
